---
title: "one parameter bootstrap - sampling without replacement for incidence data"
output: html_document
---

```{r echo=FALSE}
build_bootstrap_population = function(y, T_star){
  
  nT = y[1]; y=y[-1]; y=y[y>0]
  Q1 = sum(y == 1)
  Q2 = sum(y == 2)
  
  rho = nT/T_star
  Q0_hat = if(Q1==0&Q2==0 | rho==1 | nT==1) { 0 } else { Q1^2 / ( nT/(nT-1)*2*Q2 + rho/(1-rho)*Q1 ) }
  
  C_hat = ifelse(Q1==0&Q2==0, 1, 1-Q1/nT*(1-rho)*(nT-1)*Q1/((nT-1)*Q1+2*Q2))
  lamdba_hat = ifelse(rho==1, 0, (1-C_hat) / sum(y/nT*(1-rho)^(y/rho)))
  
  M_obs_hat = if(rho==0) { 0 } else { y/rho*(1-lamdba_hat*(1-rho)^(y/rho)) } %>% ceiling
  M_obs_hat[M_obs_hat>T_star]=T_star
  M_unobs_hat = if(Q0_hat==0) { 0 } else { rep(T_star * (1-C_hat)/Q0_hat, ceiling(Q0_hat)) } %>% ceiling
  bootstrap_population = c(T_star, M_obs_hat, M_unobs_hat)
  
  return(bootstrap_population)
  
}
```

build_bootstrap_population(y, T_star)

To estimate the bootstrap population of an incidence sample which was drawn without replacement.

- y: a vector of incidence-based sample frequencies (1st entry must be the number of sampling unit, T).

- T_star: The total sampling units in the population.

- return: a vector consisting of Mi, the number of sampling units in which species i can be detectd in the bootstrap population (1st entry is T_star).

EXAMPLES --------
```{r}
library(magrittr)
load("bird.rda")
bird_north = c(ncol(bird$inci$North.site), bird$inci$North.site %>% rowSums %>% as.vector)
build_bootstrap_population(bird_north, 100)
```